\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual Multi-Loop Integrands

### 2023-09-21 notes/2loopNLSM.tex
Starting to drop YM numbers in where needed.

Given the close ties between pion and gluon scattering for trees and
at one loop, the existence of the two-loop pion numerator prompts us
to investigate the most general local numerator for YM, without any of
the loop power counting assumptions of Ref.~\cite{Bern:2015ooa}.  We
follow the same general procedure as in \cref{sec:pions}, again
identifying the double-box and penta-triangle as the
Jacobi basis graphs and building a the most general ansatz for each of
their numerators compatible with the assumptions in
\cref{sec:bootstrap}.  Because we are now considering pure
Yang-Mills, each monomial in the local ansatz must consist of five
Lorentz scalar dot product s instead of the six for NLSM, and each
monomial must be linear in each of the four external gluon
polarizations.  Thus, the numerator ansatz for both diagrams will be
built from terms of the form:
\begin{equation}
  N^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisDoubleBox} \right]
  \text{ and }
  N^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]
  \in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
  \label{eq:ym-basis}
\end{equation}
where the $k_i$ take the same definition as described near
\cref{eq:scalar-basis}.  In our labeling of the two loop Jacobi-basis
diagrams, shown in \cref{eq:jacobi-basis}, we find that the power
counting bound proposed by Bern, Davies, and Nohle leads to an initial
ansatz with 10,000 terms in the double-box, and 9849 terms for the
penta-triangle.  Without power counting restrictions, both the
double-box and the penta-triangle ansatz have an ansatz with 10,010
terms each.  Imposing diagram automorphisms and maximal-cut gauge
invariance on the two basis diagrams, we reduce the number of terms to
XX for the double-box, and YY for the penta-triangle.  In
Ref.~\cite{Bern:2015ooa}, the unitarity matching constraints were
imposed using a spanning set of minimal physical cuts, shown in
\cref{fig:ym-spanning}.  Instead of also directly going to the
spanning cuts, we work within the framework of the Method of Maximal
Cuts \cite{Bern:2007ct} in order to identify the simplest cut that is in
tension with the kinematic Jacobi relations.

>>>>

Given the close ties between pion and gluon scattering for trees and
at one loop, the existence of the two-loop pion numerator prompts us
to investigate the most general local numerator for YM, without any of
the loop power counting assumptions of Ref.~\cite{Bern:2015ooa}.  We
follow the same general procedure as in \cref{sec:pions}, again
identifying the double-box and penta-triangle as the
Jacobi basis graphs and building a the most general ansatz for each of
their numerators compatible with the assumptions in
\cref{sec:bootstrap}.  Because we are now considering pure
Yang-Mills, each monomial in the local ansatz must consist of five
Lorentz scalar dot product s instead of the six for NLSM, and each
monomial must be linear in each of the four external gluon
polarizations.  Thus, the numerator ansatz for both diagrams will be
built from terms of the form:
\begin{equation}
  N^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisDoubleBox} \right]
  \text{ and }
  N^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]
  \in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
  \label{eq:ym-basis}
\end{equation}
where the $k_i$ take the same definition as described near
\cref{eq:scalar-basis}.  Without any power counting restrictions
imposed, both the double-box and the penta-triangle have an ansatz
with 10,010 terms each.  Imposing diagram automorphisms and
maximal-cut gauge invariance on the two basis diagrams, we reduce the
number of terms to 2235 for the double-box, and 4133 for the
penta-triangle.  In Ref.~\cite{Bern:2015ooa}, the unitarity matching
constraints were imposed using a spanning set of minimal physical
cuts, shown in \cref{fig:ym-spanning}.  Instead of also directly going
to the spanning cuts, we work within the framework of the Method of
Maximal Cuts \cite{Bern:2007ct} in order to identify the simplest cut
that is in tension with the kinematic Jacobi relations.
